---
title: "homework5"
author: "杜毓凡"
date: "2017年2月21日"
output: html_document
---
```{r echo=FALSE}
library(magrittr)
load(url("https://storage.googleapis.com/r_rookies/straw_hat_df.RData"))
```
```{r echo=FALSE}
print(straw_hat_df)
```


#使用 %>% 簡化這段程式
###簡化前
load(url("https://storage.googleapis.com/r_rookies/straw_hat_df.RData"))  
this_year <- as.numeric(format(Sys.Date(), '%Y'))  
birth_year <- this_year - straw_hat_df$age  
birth_date_chr <- paste(birth_year, straw_hat_df$birthday, sep = "-")  
straw_hat_df$birth_date <- as.Date(birth_date_chr)  

###簡化後
```{r}
straw_hat_df$birth_date<- Sys.Date() %>%
  format("%Y") %>%
  as.numeric() %>%
  "-"(straw_hat_df$age) %>%
  paste(. ,straw_hat_df$birthday, sep ="-" ) %>%
  as.Date()
```
```{r echo=FALSE}
print(straw_hat_df)
```

#計算 BMI 將 bmi 變數加入 data frame
```{r}
heights <- c(173, 168, 171, 189, 179)  
weights <- c(65.4, 59.2, 63.6, 88.4, 68.7)  
heights_and_weights <- data.frame(heights, weights)  
```
```{r echo=FALSE}
print(heights_and_weights)
```
```{r}
heights <- c(173, 168, 171, 189, 179)
weights <- c(65.4, 59.2, 63.6, 88.4, 68.7)
heights_and_weights <- data.frame(heights, weights)

BMI<-weights/((heights/100)^2) 
heights_and_weights<- cbind(heights_and_weights, BMI)
```
```{r echo=FALSE}
print(heights_and_weights)
```